---
title: "Presentation Shiny Application"
author: "Sandra Rairán"
date: "9/11/2020"
output: ioslides_presentation
---

## About Shiny Application

1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

- code reactive
`{ datasetInput <- reactive({
switch(input$dataset,
"mtcars" = mtcars,
"pressure" = pressure,
"cars" = cars)
})}`

## How to use the application

The application is running on:
 https://sandrarairan.shinyapps.io/proyecto3_appshiny/

1. Selector for choosing dataset and Numeric entry for number of observation to view
2. Select tabPanel View
3. Select tabPanel View and return the requested dataset, declaring datasetInput as a reactive expression
4. Select tabPanel Str, information about dataset



## str Dataset Cars
#### Speed and Stopping Distances of Cars
- Description
The data give the speed of cars and the distances taken to stop. Note that the data were recorded in the 1920s.

- Format
A data frame with 50 observations on 2 variables.

[,1]	speed	numeric	Speed (mph)
[,2]	dist	numeric	Stopping distance (ft)
Source
Ezekiel, M. (1930) Methods of Correlation Analysis. Wiley.

- References
McNeil, D. R. (1977) Interactive Data Analysis. Wiley.




```{r echo=FALSE,message=FALSE}
str(cars)
```



## str Dataset pressure
#### Vapor Pressure of Mercury as a Function of Temperature
- Description
Data on the relation between temperature in degrees Celsius and vapor pressure of mercury in millimeters (of mercury).


- Format
A data frame with 19 observations on 2 variables.

[, 1]	temperature	numeric	temperature (deg C)
[, 2]	pressure	numeric	pressure (mm)
Source
Weast, R. C., ed. (1973) Handbook of Chemistry and Physics. CRC Press.

_ References
McNeil, D. R. (1977) Interactive Data Analysis. New York: Wiley.

```{r echo=FALSE,message=FALSE}
str(pressure)
```

